Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-10 ppdp24/examples.tex
checkpoint

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
also shown. We present the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT ($\ttt{OT4}$), definable using $\ttt{OT}$, as
  per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
$$
\mathtt{decode(andgmw("gate0",encodegmw("s1"),encodegmw("s2")))}
$$
\end{example}

>>>>

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
also shown. We present the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT ($\ttt{OT4}$), definable using $\ttt{OT}$, as
  per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
decode(andgmw("gate0",encodegmw("s1"),encodegmw("s2")))
\end{verbatimtab}
\end{example}

\begin{comment}
\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\decodegmw(\andgmw(z,\flip{x},\flip{y})) \redxs \\
  (\prog_1,\decodegmw(\mesg{z})) \redxs (\prog_2,())
  \end{array}
  $$
  Define:
  \begin{mathpar}
    X \defeq
    \{ \elab{\flip{x}}{2}, \elab{\flip{y}}{1}, \elab{\flip{y}}{2}, \rvl{1}, \rvl{2} \}

    O \defeq  \{ \out{1}, \out{2} \}
  \end{mathpar}
  Then:
  $$
  \sep{\progtt(\prog_1)}{\{ \elab{\mesg{z}}{2} \}}{\{ \elab{\flip{x}}{1}, \elab{\flip{y}}{1}\}}
  $$
  and:
  $$
  \margd{\progtt(\prog_2)}{(\{ \elab{\flip{x}}{1} \}|\store_{X \cup O})} =
    \margd{\progtt(\prog_2)}{(\{ \elab{\flip{x}}{1} \}|\store_O)}
  $$
\end{lemma}

\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\decodegmw(\andgmw(z,\flip{x},\flip{y})) \redxs \\
  (\prog_1,\decodegmw(\mesg{z})) \redxs (\prog_2,())
  \end{array}
  $$
  Define:
  \begin{mathpar}
    X \defeq
    \{ \elab{\flip{x}}{2}, \elab{\flip{y}}{1}, \elab{\flip{y}}{2}, \rvl{1}, \rvl{2} \}

    O \defeq  \{ \out{1}, \out{2} \}
  \end{mathpar}
  Then:
  %$$
  %\sep{\progtt(\prog_1)}{\{ \elab{\mesg{z}}{2} \}}{\{ \elab{\flip{x}}{1}, \elab{\flip{y}}{1}\}}
  %$$
  %and:
  $$
  \begin{array}{c}
    \margd{\progtt(\prog_2)}{(\cod{\store(\elab{\flip{x}}{1})\ \exor\ \store(\elab{\flip{x}}{2})}|\store_{X \cup O})} =\\
    \margd{\progtt(\prog_2)}{(\cod{\store(\elab{\flip{x}}{1})\ \exor\ \store(\elab{\flip{x}}{2})}|\store_O)}
  \end{array}
  $$
  $$
  \sep{\progtt(\prog_2)}{(\cod{\store(\elab{\flip{x}}{1})\ \exor\ \store(\elab{\flip{x}}{2})}) \cup O}{X}
  $$
  $$
  \sep{\progtt(\prog_2)}{\{ \macgv{x} \} \cup O}{X}
  $$
\end{lemma}
\end{comment}

\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Define:
  \begin{mathpar}
    X \defeq
    \{ \elab{\mesg{x}}{2}, \macgv{\mesg{y}}, \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \}
  \end{mathpar}
  Then:
  $$
  \sep{\progtt(\prog)}{\{ \macgv{\mesg{x}}, \macgv{\mesg{z}} \}}{X}
  $$
\end{lemma}

\begin{lemma}
  $$ (\varnothing,e) \redxs (\prog,\decodegmw(E[\mesg{x}])) $$
  $$\iov(\prog) = S \cup M$$
  $$\sep{\progtt(\prog)}{(S_H \cup \{ \macgv{\mesg{x}} \})}{(M_C \cup \{ \elab{\mesg{x}}{1}, \elab{\mesg{y}}{2} \})}$$
\end{lemma}
